### 2014-02-27 paper/formal.tex

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwsie, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

@@

We note that the definition of |erasef il| precisely captures the IFC
language's attacker model. 
%
For instance, in our case, by removing sensitive tasks and messages from the
system, we assume that that the attacker cannot observe the number of sensitive
tasks or messages.
%
While such assumptions are standard~\tocite{}, our defintions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We belive that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniqes of~\tocite{}.
  %
  We leave this extension to future work.
}

Non-inteference relies on the defintion of an attacker's observational power at
security level |l|, which is typically defined as an equivalence
relation---called |l|-equivalence---on configurations, i.e., an attacker cannot
distinguish two configurations that are |l|-equivlaent.
%
Since our erasure function captures attacker mode, we simply define this
equivalance as the syntactic-equivalence of erased configurations.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}
%

>>>>

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwise, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

@@

We note that the definition of |erasef il| precisely captures the IFC
language's attacker model. 
%
For instance, in our case, by removing sensitive tasks and messages from the
system, we assume that that the attacker cannot observe the number of sensitive
tasks or messages.
%
While such assumptions are standard~\tocite{}, our definitions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We believe that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniques of~\tocite{}.
  %
  We leave this extension to future work.
}

Non-interference relies on the definition of an attacker's observational power at
security level |l|, which is typically defined as an equivalence
relation---called |l|-equivalence---on configurations, i.e., an attacker cannot
distinguish two configurations that are |l|-equivalent.
%
Since our erasure function captures the attacker model, we simply define this
equivalence as the syntactic-equivalence of erased configurations.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}
%
